### 2022-08-17 manuscript.Rmd
Add Supplementary info (stimuli, model outputs)

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

@@

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage{orcidlink}
  - \usepackage[all]{nowidow}
  - \captionsetup[figure]{belowskip=10pt}
  - \captionsetup[figure]{font={small,stretch=1},textfont=normalfont}
  - \captionsetup[figure]{labelfont=bf,labelsep=period,name=Figure}
---

@@

We computed three models predicting P1, N170, and N400 amplitudes, respectively.
All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
We determined the most parsimonous random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20).
All models were fitted in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].

@@

```{r, table_1, include=TRUE}
# View model summaries
walk(models, function(model) {
  print(formula(model$model))
  cat("\n")
  print(model$anova)
  cat("\n")
  print(model$contrasts)
  cat("\n\n")
})
```

@@

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

@@

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage{orcidlink}
  - \usepackage[all]{nowidow}
  - \captionsetup[figure]{belowskip=10pt}
  - \captionsetup[figure]{font={small,stretch=1},textfont=normalfont}
  - \captionsetup[figure]{labelfont=bf,labelsep=period,name=Figure}
  - \captionsetup[table]{labelfont=bf,labelsep=period,textfont=bf}
  - \usepackage[export]{adjustbox}
  - \usepackage{makecell}
  - \usepackage{setspace}
---

@@

We computed three models predicting P1, N170, and N400 amplitudes, respectively.
All models included three fixed effects: (a) the phase of the experiment, coded as a repeated contrast [i.e., subtracting the first phase from the second phase and the second phase from the third phase, the intercept being the grand mean across all three phases\; @schad2020], (b) the condition of the object, coded as a scaled sum contrast (i.e., subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of phase and condition.
We determined the most parsimonous random effect structure supported by the data using the automatic procedure proposed by @matuschek2017.
This involved starting with a maximal model that contained all random parameters (intercepts, slopes, and correlations) and then iteratively removing terms as long as this did not result in a significant drop in model fit (likelihood ratio test, $p$ value cutoff = .20).
See Supplementary Results 1 for the final model syntax and model outputs.
All models were fitted in R [Version `r as.character(packageVersion("base"))`\; @R-base] using the lme4 package [Version `r as.character(packageVersion("lme4"))`\; @R-lme4] with the optimizer function *bobyqa* and a maximum of 10^6^ iterations for maximum likelihood estimation.
The model selection algorithm via likelihood ratio tests was performed using the buildmer package [Version `r as.character(packageVersion("buildmer"))`\; @R-buildmer].

@@

@@

\newpage
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}

# Supplementary Information

```{r tabs1, include=TRUE, results="asis"}
# Print table of materials
read_tsv(here("materials", "items.txt"), col_types = cols()) %>%
  mutate(
    match_ger = paste0(match_noun_ger, ", ", match_verb_ger),
    match_en = paste0("{[", match_noun_en, ", ", match_verb_en, "]}"),
    nonmatch_ger = paste0(nonmatch_noun_ger, ", ", nonmatch_verb_ger),
    nonmatch_en = paste0("{[", nonmatch_noun_en, ", ", nonmatch_verb_en, "]}"),
  ) %>%
  transmute(
    img = paste0(
      "\\includegraphics[valign=c,scale=0.245]{materials/unfamiliar/",
      item,
      ".png}"
    ),
    item = as.character(item),
    match = paste(match_ger, match_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n"),
    nonmatch = paste(nonmatch_ger, nonmatch_en, sep = "\n") %>%
      kableExtra::linebreak(align = "l", linebreaker = "\n")
  ) %>%
  apa_table(
    booktabs = TRUE,
    col.names = c(
      "Stimulus", "ID", "Matching keywords", "Non-matching keywords"
    ),
    escape = FALSE,
    longtable = TRUE,
    caption = "Unfamiliar Object Stimuli\\smallskip",
    font_size = "footnotesize"
  )
```

## Results S1. *Linear Mixed-Effects Models*

## *P1 Component (100--150 ms)*

\small
\singlespacing

```{r, ress1a, include=TRUE}
# Helper function for printing model summary, ANOVA (F tests), and contrasts
print_model_outputs <- function(model_object) {
  model <- model_object$model
  model@call$data <- NULL # Prevents cluttering the `summary` output
  print(summary(model))
  cat("\n")
  print(model_object$anova)
  cat("\nFollow-Up Contrasts (Simple Effects)\n")
  print(model_object$contrasts)
  cat("\n\n")
}

# Print model outputs
print_model_outputs(models$P1)
```

\newpage
\normalsize
\doublespacing

## *N170 Component (150--200 ms)*

\small
\singlespacing

```{r, ress1b, include=TRUE}
# Print model outputs
print_model_outputs(models$N170)
```

\newpage
\normalsize
\doublespacing

## *N400 Component (400--700 ms)*

\small
\singlespacing

```{r, ress1c, include=TRUE}
# Print model outputs
print_model_outputs(models$N400)
```
